---
title: "Project - Module 1"
output: html_document
date: "2023-10-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
sp <- read.csv("data_csv.csv")
sp
```

A reproducible time series plot with appropriate labels and with a concise explanation of the data the time series represents.
```{r}
sp.ts <- ts(sp$PE10, start = c(1881,1), end = c(2018,4), freq=12)
plot(sp.ts, xlab="Time", ylab="Shiller PE Ratio", ylim=c(0,50), bty="l")
```
This time series represents the Shiller PE Ratio (Share Price to 10 year-Earnings average Ratio). Because seasonality has an effect on supply and demand of products, using a 10 year earnings average minimizes the intra-year changes and allows for clearer visualization of the underlying long term trend.

This dataset contains monthly measurements of the Standard and Poor's 500 index levels. For additional context, the series also contains nominal and real dividend, nominal and real earnings, consumer price index, interest rates, and the Shiller PE ratio. Possible business applications include overbought and oversold market indicators and earnings-anchored valuation products.